### 2013-01-14 sections/implementation.tex
* back to 8 pages   * reduced all figure sizes to 0.9/linewidth   * removed tcpdump, wireshark, libpcap paragraph with citations
penultimate, corrections
reduced the content to 7 pages
back to 6 pages
added JSON rfc

The \ac{NFQL} architecture primarily consists of a front-end parser backed up
by an execution engine as shown in Fig. \ref{fig:architecture}. The execution
engine is the brain of \ac{NFQL} where the complete pipeline is processed. It
receives the flow query at runtime using a JSON intermediate format. The
execution engine is designed to receive this input from either a machine
running the front-end parser or a webservice that pushes the JSON from the
cloud. The execution engine is written in C, however the front-end parser can
be written in any desired language.

\begin{figure}[h!]
  \begin{center}
    \includegraphics* [width=1.0\linewidth]{nfql-architecture}
    \caption{NFQL Architecture}
    \label{fig:architecture}
  \end{center}
\end{figure}

>>>>

The \ac{NFQL} architecture primarily consists of a front-end parser backed up
by an execution engine as shown in Fig. \ref{fig:nfql-pipeline}. The execution
engine is the brain of \ac{NFQL} where the complete pipeline is processed. It
receives the flow query at runtime using a JSON \cite{rfc4627} intermediate
format. The execution engine is written in C, however the front-end parser can
be written in any desired language.

%\begin{figure}[ht!]
  %\begin{center}
    %\includegraphics* [width=0.8\linewidth]{nfql-architecture}
    %\caption{NFQL Architecture}
    %\label{fig:architecture}
  %\end{center}
%\end{figure}
